Report: Analysis of Independence between Sample Mean and Coefficient of Variation

### 2024-08-15 Code/R/RMarkdown/Report_Independence_of_Mean_and_CV.Rmd
quarto files

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}

---

@@

# Introduction
we analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution. This independence is unique to the Gamma distribution and does not apply to other common distributions.

In the context of identifying heterogeneity in SAR imaging data, two main models are used: the Gamma SAR distribution and the $G_I^0$ distribution. The Gamma SAR distribution is easier to handle and allows homogeneous areas to be identified without having to resort to the $G_I^0$ distribution.

@@

# Gamma SAR Distribution
For the Gamma SAR distribution, we simulated the data and plotted the CV versus the mean.

@@

```
The scatter plot for the Gamma SAR distribution shows a random distribution of points, indicating that the mean and CV are independent. This confirms the property of the Gamma distribution where the sample mean and CV do not reveal any correlation.

@@

where \(\beta_0\) and \(\beta_1\) are parameters, the p-value for \(\beta_1\) plays a crucial role in understanding the fit of the model and the nature of the data distribution.

@@

```{r parameters, echo=FALSE, message=FALSE, warning=FALSE}
results <- data.frame(
  Alpha = rep(c(-1.5, -3, -6, -20, -100, -200, -1000), each = 2),
  Parameter = rep(c("$\\beta_0$", "$\\beta_1$"), 7),
  Estimate = c(
    -0.04401, 0.37712,
    -0.067687, 0.219549,
    0.017231, 0.084623,
    0.055379, 0.020427,
    0.062530, 0.004908,
    0.063711, 0.002681,
    0.066356, -0.000558
  ),
  StdError = c(
    0.00266, 0.00300,
    0.002597, 0.002595,
    0.001935, 0.001931,
    0.001373, 0.001370,
    0.001215, 0.001214,
    0.001181, 0.001180,
    0.001185, 0.001184
  ),
  tvalue = c(
    -16.55, 125.71,
    -26.06, 84.62,
    8.904, 43.825,
    40.34, 14.91,
    51.450, 4.045,
    53.933, 2.272,
    56.012, -0.472
  ),
  pvalue = c(
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "5.28e-05",
    "<2e-16", "0.0231",
    "<2e-16", "0.637"
  ),
  stringsAsFactors = FALSE  # Asegúrate de que los datos de texto no se conviertan en factores
)

# Define los nombres de las columnas
colnames(results) <- c("$\\alpha$", "\\textbf{Parameter}", "\\textbf{Estimate}", "\\textbf{Std. Error}", "\\textbf{$t$ Value}", "\\textbf{$p$ Value}")

# # Formatea los números
# results$Estimate <- sprintf("$%.5f$", results$Estimate)
# results$StdError <- sprintf("$%.5f$", results$StdError)
# results$tvalue <- sprintf("$%.2f$", results$tvalue)
# results$pvalue <- ifelse(results$pvalue == "<2e-16", "< 2e-16", results$pvalue)
# 
# # Imprime los resultados para verificar
# print(results)
#results$Alpha <- sprintf("$%.1f$", results$Alpha)
results[] <- lapply(names(results), function(col_name) {
  x <- results[[col_name]]
  if (is.numeric(x)) {
    if (col_name == "Alpha") {
      formatted_numbers <- sprintf("$\\scriptstyle %d$", x)  # Estilo específico para Alpha
    } else {
      if (all(x %% 1 == 0)) {
        formatted_numbers <- sprintf("$%d$", x)
      } else {
        formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
      }
    }
    return(formatted_numbers)
  } else {
    return(x)  # Mantiene los valores de texto sin cambios
  }
})

@@

## Interpretation of p-Values for \(\beta_1\)

### High $p$-Value for \(\beta_1\)

- **Implication**: A high p-value (typically greater than 0.05) for \(\beta_1\) suggests that the coefficient \(\beta_1\) is not significantly different from zero. This implies that the relationship between the mean (\(\bar{x}\)) and the coefficient of variation  in the data can be explained by the Gamma SAR distribution.

- **Interpretation**: When \(\beta_1\) is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution. In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.

### Low $p$-Value for \(\beta_1\)

- **Implication**: A low p-value (typically less than 0.05) for \(\beta_1\) indicates that \(\beta_1\) is significantly different from zero. This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.

- **Interpretation**: When \(\beta_1\) is statistically significant, it implies that the data is better described by the \(G_I^0\) distribution . In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics. Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the \(G_I^0\) distribution. The parameter \(\alpha\) of the \(G_{I^0}\) distribution, which approaches $-1$ in extreme cases, captures this dependency.

>>>>

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}
---

@@

# Introduction

We analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.

Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution. The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution.

@@

# Gamma SAR Distribution

For the Gamma SAR distribution, we simulated the data and plotted the CV versus the mean.

@@

The scatter plot for the Gamma SAR distribution shows a random distribution of points, indicating that the mean and CV are independent. This confirms the property of the Gamma distribution where the sample mean and CV do not reveal any correlation.

@@

where $\beta_0$ and $\beta_1$ are parameters, the p-value for $\beta_1$ plays a crucial role in understanding the fit of the model and the nature of the data distribution.

@@

```{r parameters, echo=FALSE, message=FALSE, warning=FALSE}
results <- data.frame(
  Alpha = rep(c(-1.5, -3, -6, -20, -100, -200, -1000), each = 2),
  Parameter = rep(c("$\\beta_0$", "$\\beta_1$"), 7),
  Estimate = c(
    -0.04401, 0.37712,
    -0.067687, 0.219549,
    0.017231, 0.084623,
    0.055379, 0.020427,
    0.062530, 0.004908,
    0.063711, 0.002681,
    0.066356, -0.000558
  ),
  StdError = c(
    0.00266, 0.00300,
    0.002597, 0.002595,
    0.001935, 0.001931,
    0.001373, 0.001370,
    0.001215, 0.001214,
    0.001181, 0.001180,
    0.001185, 0.001184
  ),
  tvalue = c(
    -16.55, 125.71,
    -26.06, 84.62,
    8.904, 43.825,
    40.34, 14.91,
    51.450, 4.045,
    53.933, 2.272,
    56.012, -0.472
  ),
  pvalue = c(
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "5.28e-05",
    "<2e-16", "0.0231",
    "<2e-16", "0.637"
  ),
  stringsAsFactors = FALSE  # 
)

# 
colnames(results) <- c("$\\alpha$", "\\textbf{Parameter}", "\\textbf{Estimate}", "\\textbf{Std. Error}", "\\textbf{$t$ Value}", "\\textbf{$p$ Value}")

#results$Alpha <- sprintf("$%.1f$", results$Alpha)
results[] <- lapply(names(results), function(col_name) {
  x <- results[[col_name]]
  if (is.numeric(x)) {
    if (col_name == "Alpha") {
      formatted_numbers <- sprintf("$\\scriptstyle %d$", x)  # Estilo específico para Alpha
    } else {
      if (all(x %% 1 == 0)) {
        formatted_numbers <- sprintf("$%d$", x)
      } else {
        formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
      }
    }
    return(formatted_numbers)
  } else {
    return(x)  # 
  }
})

@@

## Interpretation of p-Values for $\beta_1$

### High $p$-Value for $\beta_1$

-   **Implication**: A high $p$-value (typically greater than 0.05) for $\beta_1$ suggests that the coefficient $\beta_1$ is not significantly different from zero. This implies that the relationship between the mean ($\bar{x}$) and the coefficient of variation in the data can be explained by the Gamma SAR distribution.

-   **Interpretation**: When $\beta_1$ is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution. In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.

### Low $p$-Value for $\beta_1$

-   **Implication**: A low $p$-value (typically less than 0.05) for $\beta_1$ indicates that $\beta_1$ is significantly different from zero. This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.

-   **Interpretation**: When $\beta_1$ is statistically significant, it implies that the data is better described by the $G_I^0$ distribution . In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics. Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the $G_I^0$ distribution. The parameter $\alpha$ of the $G_{I^0}$ distribution, which approaches $-1$ in extreme cases, captures this dependency.

### 2024-08-15 Text/Reports/article-report/R0-article-report.Rmd
quarto files

---
title: "Report: Analysis of Independence between Sample Mean and Coefficient of Variation"
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)

#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")
source("../MainFunctions/gi0_sample.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

@@

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

\newcommand{\bias}{\operatorname{Bias}}

@@

We analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.

Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution. The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution.

@@

To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.

@@

source("../MainFunctions/gamma_sar_sample.R")

@@

source("../MainFunctions/gamma_sar_sample.R")
source("../MainFunctions/entropy_gamma_sar.R")
source("../MainFunctions/entropy_gI0.R")
source("../MainFunctions/gi0_sample.R")

@@

# 
summary(model)

@@

## Interpretation of p-Values for $\beta_1$

### High $p$-Value for $\beta_1$

-   **Implication**: A high $p$-value (typically greater than 0.05) for $\beta_1$ suggests that the coefficient $\beta_1$ is not significantly different from zero. This implies that the relationship between the mean ($\bar{x}$) and the coefficient of variation in the data can be explained by the Gamma SAR distribution.

-   **Interpretation**: When $\beta_1$ is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution. In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.

### Low $p$-Value for $\beta_1$

-   **Implication**: A low $p$-value (typically less than 0.05) for $\beta_1$ indicates that $\beta_1$ is significantly different from zero. This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.

-   **Interpretation**: When $\beta_1$ is statistically significant, it implies that the data is better described by the $G_I^0$ distribution . In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics. Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the $G_I^0$ distribution. The parameter $\alpha$ of the $G_{I^0}$ distribution, which approaches $-1$ in extreme cases, captures this dependency.

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
bibliography: ../../Common/references.bib
header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=1pt, 
        belowskip=1pt,
        singlelinecheck=off,
        justification=centering}   
biblio-style: apsr
title: "Report: Analysis of Independence between Sample Mean and Coefficient of Variation"
thanks: ""
author:
- name: J. Alpala
  affiliation: 
abstract: "We analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.
Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution. The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution."
keywords: "Gamma distribution, coefficient of variation, mean, heterogeneity, SAR "
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: libertine
fontsize: 11pt
# spacing: double
endnote: no
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE,
                      fig.path='figs/',
                      cache.path = '_cache/',
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })

library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")

source("../../../Code/R/MainFunctions/van_es_estimator.R")
source("../../../Code/R/MainFunctions/correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/vasicek_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../../../Code/R/Programs/read_ENVI_images.R")

@@

@@

Synthetic Aperture Radar (SAR) technology has become essential for environmental monitoring and disaster management. It provides valuable images under various conditions, including day or night and weather situations&nbsp;\cite{Moreira2013,Mu2019}.
However, the effective use of SAR data depends on a thorough understanding of its statistical properties because it is corrupted by speckle.
This noise-like interference effect is inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.

Speckle in intensity format is non-Gaussian. Thus, SAR data require reliable statistical models for accurate processing. 
The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
Gamma law as the limiting case for fully-developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.

Our work aims to improve the identification of potential roughness features in SAR intensity data.
Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions.

In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous returns, particularly between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.

# Background {#sec:Background}

## Statistical Modeling of Intensity SAR data

The primary models for intensity SAR data include the Gamma and
$\mathcal{G}_I^0$ distributions [@Frery1997]. The first is suitable for
fully-developed speckle and is a limiting case of the second model. This
is interesting due to its versatility in accurately representing regions
with different roughness properties [@Cassetti2022]. We denote
$Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and
$Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows
the distributions characterized by the respective probability density
functions (pdfs): \begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where $\mu > 0$ is the mean, $\gamma > 0$ is the scale,
$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of looks
(either nominal or estimated, thus not restricted to integer values),
$\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the
indicator function of the set $A$.

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation} provided $\alpha <-r$, and infinite otherwise. Therefore,
assuming $\alpha<-1$, its expected value is \begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

Although the $\mathcal{G}_I^0$ distribution is defined by the parameters
$\alpha$ and $\gamma$, in the SAR literature \cite{Nascimento2010} the
texture $\alpha$ and the mean $\mu$ are usually used.
Reparametrizing \eqref{E:gi01} with $\mu$, and denoting this model as
$G_I^0$ we obtain: \begin{equation}
        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

@@

To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.
To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.

@@

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")

@@

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")

@@

# 
#summary(model)

@@

```{=html}
<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
```
